Automated Formal Synthesis of Digital Controllers for State-Space Physical Plants

### 2017-01-24 cav2017/cav2017.tex
updated introduction

We describe and evaluate two approaches for synthesizing digital controllers 
for state-space physical plants. Both approaches consider a counterexample 
guided inductive synthesis (CEGIS) loop. In the first approach, 
we devise a digital controller that stabilises the system; then, we verify its 
potential safety by unfolding the dynamics of the system and checking for 
a completeness threshold. In the second approach, we employ abstract acceleration
to accelerate the dynamics forward instead of symbolically unwinding the 
transition relation~\cite{cattaruzza2015unbounded}.

@@

In summary, this paper makes the following original contributions.
%
\begin{itemize}

\item We design and implement two approaches to synthesize 
  digital feedback control architectures for physical plants, 
	considering dynamical equations with inputs that evolves over 
	a continuous state space. In both approaches, we apply CEGIS to 
	devise a digital controller that stabilizes the system and we then
	we verify safety by means of either forward reachability analysis 
	via dynamics unfolding or invariant set generation via 
	abstract acceleration.

\item We provide experimental results showing that our approaches
  are able to efficiently synthesize stable and safe controllers 
	for a set of intricate physical plant models taken from the digital 
	control literature: the median runtime for our benchmark
  set is \textcolor{red}{$XXX$}s, i.e., most controllers can be synthesized in less
  than \textcolor{red}{$XXX$} seconds.

\end{itemize}

>>>>

We describe and evaluate two approaches for synthesizing digital controllers 
for state-space physical plants. Both approaches consider a counterexample 
guided inductive synthesis (CEGIS) loop. In the first approach, 
we devise a digital controller that stabilises the system; then, we verify its 
potential safety by unfolding the dynamics of the system and checking for 
a completeness threshold. In the second approach, we employ abstract acceleration
to accelerate the dynamics forward instead of symbolically unwinding the 
transition relation~\cite{cattaruzza2015unbounded}. We provide experimental results 
showing that both approaches are able to efficiently synthesize stable and safe controllers 
for a set of intricate physical plant models taken from the digital 
control literature: the median runtime for our benchmark
set is \textcolor{red}{$XXX$}s, i.e., most controllers can be synthesized in less
than \textcolor{red}{$XXX$} seconds.

@@

%In summary, this paper makes the following original contributions.
%
%\begin{itemize}

%\item We design and implement two approaches to synthesize 
%  digital feedback control architectures for physical plants, 
%	considering dynamical equations with inputs that evolves over 
%	a continuous state space. In both approaches, we apply CEGIS to 
%	devise a digital controller that stabilizes the system and we then
%	we verify safety by means of either forward reachability analysis 
%	via dynamics unfolding or invariant set generation via 
%	abstract acceleration.

%\item We provide experimental results showing that our approaches
%  are able to efficiently synthesize stable and safe controllers 
%	for a set of intricate physical plant models taken from the digital 
%	control literature: the median runtime for our benchmark
%  set is \textcolor{red}{$XXX$}s, i.e., most controllers can be synthesized in less
%  than \textcolor{red}{$XXX$} seconds.

%\end{itemize}
